---
title: "Compile Tree by Site Series Info"
author: "Kiri Daust/Will MacKenzie"
date: "04/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
require(dplyr)
require(ggplot2)
require(MASS)
require(magrittr)
require(foreach)
require(reshape2)
require(reticulate)
require(Rcpp)
library(gridExtra)
library(data.table)
library(scales)
library(tidyr)
library(magrittr)
library(ggthemes)
library(flextable)
require(rgdal)
require(tmap)
library(sf)
```

Load data

```{r load data sets}
##Set drive with cloud data
if(dir.exists("C:/users/whmacken/Sync")){
  cloud_dir <- "C:/users/whmacken/Sync/CCISS_data/CommonTables/"
}else{
  cloud_dir <- "C:/Users/kirid/Sync/CCISS_data/CommonTables/"
}

###Read in data
## 1. All BGCS (info table from USA_BGC project)
  bgc <- fread(paste0(cloud_dir,"All_BGCs_v11_21.csv"),data.table = F)

## 2. All Site Series (info table from from USA_BGC project)
  ss <- fread(paste0(cloud_dir, "WNA_SSeries_v11.csv"),data.table = F)

## 3. All Edatopic (info table from USA_BGC project)
  eda <- fread(paste0(cloud_dir, "Edatopic_v11_20.csv"),data.table = F)

## 4. All aSMR (modelled in aSMR_X_rSMR project)
  asmr <- fread(paste0(cloud_dir, "modelled_WNAv11_rSMR_aSMR_grid_HalfStep.csv"),data.table = F)

## 5. All Feasibility (in part modelled in TreeSuitabilityPrediction project)

  feasible <- fread(paste0(cloud_dir, "Feasibility_v11_21.csv"),data.table = F)

  ## 6. All Site Index (modelled in SIBEC_Modelled project)
 sibec <- fread(paste0(cloud_dir, "PredSI_May2020.csv"),data.table = F)
  
```
   
   
   SuitTable <- fread("InputsGit/Feasibility_v11_21.csv") ##tree spp suitability
SuitTable <- unique(SuitTable)

colnames(SuitTable)[2:4] <- c("SS_NoSpace","Spp","Suitability")
SuitTable <- SuitTable[,c("BGC","SS_NoSpace","Spp","Suitability")]

SIBEC <- fread("InputsGit/PredSI_May2020.csv") ###import SI data (currently from BART)

SIBEC <- SIBEC[,c("SS_NoSpace","Spp","SIPred")] %>% set_colnames(c("SS_NoSpace","TreeSpp","MeanPlotSiteIndex"))

if(file.exists(paste0(cloud_dir,"CCISSPred.Rdata"))){
  load(paste0(cloud_dir,"CCISSPred.Rdata"))
}else{
  ### run CCISS function to predict Site Series
  load(paste0(cloud_dir, "WNAv11_35_VAR_SubZone_ranger.Rdata"))
  Edatope <- fread("./InputsGit/Edatopic_v11_20.csv",data.table = F)
  rawDat <- fread(paste0(cloud_dir,"PortfolioFiles/",inputDatName),data.table = F)
  CCISSPred <- CCISS_Spp(Y1 = rawDat,BGCmodel = BGCmodel,E1 = Edatope)
  save(CCISSPred, file = paste0(cloud_dir,"CCISSPred.Rdata"))
}

SSPredFull <- CCISSPred[[1]]
colnames(SSPredFull)[1] <- "MergedBGC"
SSPredFull <- SSPredFull[grep("01",SSPredFull$SSCurrent),]
SSPredFull$CurrBGC <- gsub("/.*","", SSPredFull$SSCurrent)

#SSPredFull <- fread("InputsGit/SunshineSSPred.csv") ##Import SS predictions from CCISS tool: must have columns MergedBGC, Source, SS_NoSpace, SSprob, SSCurrent, FuturePeriod, SiteNo
SSPredFull <- SSPredFull[,c("MergedBGC", "Source", "SS_NoSpace", "SSprob", "SSCurrent", 
                          "FuturePeriod", "SiteNo","CurrBGC")]

##remove cases where not all timeperiods available
SSPredFull <- as.data.table(SSPredFull)
temp <- SSPredFull[,.(Num = length(unique(FuturePeriod))), by = c("SiteNo","SSCurrent")]
temp <- temp[Num == 3,-c("Num")]
SSPredFull <- SSPredFull[temp,on = c("SiteNo","SSCurrent")]
SSPredFull[,SiteNo := as.numeric(SiteNo)]

analUnits <- fread(paste0(cloud_dir,"PortfolioFiles/AnalysisUnits.csv"))
setkey(SSPredFull, SiteNo)
setkey(analUnits, ID1)
SSPredFull <- SSPredFull[analUnits]

SSPredSave <- SSPredFull
```

