---
title: "Check Table Congruity for CCISS information Tables"
author: "Kiri Daust/Will MacKenzie"
date: "04/06/2020"
output: html_document
---
This code compares the information tables of CCISS 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
require(dplyr)
require(ggplot2)
require(MASS)
require(magrittr)
require(foreach)
require(reshape2)
require(reticulate)
require(Rcpp)
library(gridExtra)
library(data.table)
library(scales)
library(tidyr)
library(magrittr)
library(ggthemes)
library(flextable)
require(rgdal)
require(tmap)
library(sf)
```

Load data

```{r load data sets}
##Set drive with cloud data
if(dir.exists("F:/OneDrive - Government of BC/CCISSv12/")){
  cloud_dir <- "F:/OneDrive - Government of BC/CCISSv12/latest_CCISS_tool_files/"
}else{
  cloud_dir <- "C:/Users/kirid/Sync/CCISS_data/CommonTables/"
}

###Read in data
## 0. List of retired BGCs and site series
retiredSS <- fread(paste0(cloud_dir, "Retired_SS.csv")) %>% dplyr::select(Retire, SS_NoSpace)
retiredBGC <- fread(paste0(cloud_dir,"All_BGCs_Info_v12_2.csv")) %>% filter(Retire == 'x') %>% dplyr::select(BGC) 

## 1. All BGCS (info table from USA_BGC project)
bgc_modelled <- fread(paste0(cloud_dir,"AllmodelledBGCs_v12_2.csv"))
bgc_modelled$modelled <- "yes"
bgc.info <- fread(paste0(cloud_dir,"All_BGCs_Info_v12_2.csv")) %>% filter(!Retire == 'x') %>% 
  dplyr::select(Source, Zone, BGC, DataSet)

## 2. All Site Series (info table from from USA_BGC project)
ss.list <- fread(paste0(cloud_dir, "WNA_SSeries_v12_10.csv"))#%>% filter(!Retire == 'x') %>% dplyr::select(-Retire)
#ss.list <- ss[,.(BGC, SS_NoSpace)]

## 3. All Edatopic (info table from USA_BGC project)
eda <- fread(paste0(cloud_dir, "Edatopic_v12_10.csv")) 
## remove retired site series
setkey(eda, SS_NoSpace)
setkey(retiredSS, SS_NoSpace)
ss_eda <- merge(eda, retiredSS, all = T) #%>% filter(is.na(Retire))
#fwrite(ss_eda,paste0(cloud_dir, "Edatopic_v12_2.csv")) 
eda_small <- ss_eda[,.(SS_NoSpace,Edatopic)]
eda.space <- fread("./inputs/edatopic_space.csv")

## 4. All aSMR (modelled in aSMR_X_rSMR project)
asmr <- fread(paste0(cloud_dir, "modelled_rSMR_aSMR_grid_HalfStep_WNAv12_2.csv"))

## 5. All Feasibility (in part modelled in TreeSuitabilityPrediction project)
feasible <- fread(paste0(cloud_dir, "Feasibility_v12_10.csv"))# %>% filter(!Retire == 'x')
feasible.add.info <- full_join(feasible, bgc.info, by = "BGC") %>% dplyr::select(DataSet, Source, Zone, BGC, SS_NoSpace,SppVar, Feasible) 
feas.list <- feasible.add.info[,.(SS_NoSpace, SppVar, Feasible)]

## 6. All Site Index (modelled in SIBEC_Modelled project)
sibec <- fread(paste0(cloud_dir, "PredSI_May2020.csv"))

## 7. SIBEC 2013 summarised
#sibec13 <- fread(paste0(cloud_dir, "SIBEC_2013_Summary.csv"))
#colnames(sibec13)[2:3] <- c("Spp","SI13")
```
   

These are the duplicates in each table

```{r duplicates}
outFold <- "./Duplicated/"
any(duplicated(bgc_modelled))
any(duplicated(bgc.info))
### site series
any(duplicated(ss.list))
ss.list[, fD := .N > 1, by = .(SS_NoSpace)]
fwrite(ss.list[(fD)], paste0(outFold,"SiteSeries_duplicated.csv"))
ss.list[,fD := NULL]
ss.list <- unique(ss.list)
### edatopic
any(duplicated(eda_small))
eda_small[,fD := .N > 1, by = .(SS_NoSpace,Edatopic)]
fwrite(eda_small[(fD)],paste0(outFold,"Edatopic_duplicated.csv"))
eda_small <- unique(eda_small[,!"fD"])

###feasibility
any(duplicated(feas.list))
feas.list[,fD := .N > 1, by = .(SS_NoSpace,SppVar)]
fwrite(feas.list[(fD)],paste0(outFold,"Feasibility_duplicated.csv"))
feas.list <- unique(feas.list[,!"fD"], by = c("SS_NoSpace","SppVar"))
# feasible <- feasible %>% distinct()
#fwrite(feasible, paste0(cloud_dir, "Feasibility_v12_9.csv"))
### sibec
# any(duplicated(sibec))
# sibec[,fD := .N > 1, by = .(SS_NoSpace,Spp)]
# fwrite(sibec[(fD)], paste0(outFold,"Sibec_duplicated.csv"))
# sibec <- unique(sibec[,!"fD"], by = c("SS_NoSpace","Spp"))

```

```{r find_missing}

### 1. compare BGC_modelled with BGC list
setkey(bgc_modelled,BGC)
setkey(bgc.info, BGC)
### matching BGC in model and list of units
bgc_compare <- merge(bgc_modelled, bgc.info, all = T)
bgc_no.model <- bgc_compare[is.na(modelled),.(BGC)]
bgc_no.info <- bgc_compare[is.na(Source),.(BGC)]

###matching modelled BGCs and Site Series
setkey(bgc_modelled,BGC)
setkey(ss.list,BGC,SS_NoSpace)
bgc_ss <- merge(bgc_modelled, ss.list, all = T)
bgc_NoSS <- bgc_ss[is.na(BGC),.(SS_NoSpace)]
ss_NoBGC <- bgc_ss[is.na(SS_NoSpace),.(BGC)]

###matching site series and edatopic space
setkey(eda_small,SS_NoSpace)
ss.list$current <- "yes"
ss_eda2 <- merge(ss.list, eda_small, all = T) %>% filter(!is.na(current))
ss_noeda <- ss_eda2[is.na(Edatopic),.(SS_NoSpace)]

ss_eda2 <- ss_eda2 %>% dplyr::select(Source, BGC, SS_NoSpace, Edatopic, SpecialCode) 
fwrite(ss_eda2, paste0(cloud_dir, "Edatopic_v12_test.csv"))


###missing edatopic space
# BGC.eda.used <- ss_eda2 %>% dplyr::select(BGC, Edatopic) %>% distinct() 
# BGC.eda.used <- left_join(eda.space, BGC.eda.used)

eda.matrix <- ss_eda2 %>% filter(!is.na(Edatopic)) %>% dplyr::select(BGC, Edatopic) %>% count(BGC, Edatopic) %>%  
  pivot_wider(id_cols = "BGC", names_from = "Edatopic", values_from = "n", values_fill = 99)
eda.noexpected <- c("C0", "D0", "E0", "C1", "D1", "E1", "D2", "E2", "D3", "E3") #positions commonly unfilled
##can reduce list to identify specific SMR positions - then add working units to fill
eda.missing <- eda.matrix %>% pivot_longer(!BGC, names_to = "Edatopic", values_to = "count") %>% filter(count == 99) %>% 
  filter(!Edatopic %in% eda.noexpected) 
#%>%   filter(Edatopic == "D5")

setkey(eda.space,Edatopic)
setkey(eda_small, Edatopic)
eda.miss <- merge(eda.space, eda_small, all = T) %>% filter(is.na(Edatopic))
#eda.miss <- merge(eda.space, ss_eda, all = T) %>% filter(is.na(Edatopic))


### missing aSMR by BGC
setkey(asmr, BGC)
bgc_asmr <- merge(bgc.info, asmr, all = T)
asmr_NoBGC <- bgc_asmr[is.na(rSMR0),.(BGC)]
bgc_NoASMR <- bgc_asmr[is.na(Zone),.(BGC)]

eda_nospace <- bgc_asmr[is.na(rSMR0),.(BGC)]
bgc_NoASMR <- bgc_asmr[is.na(Zone),.(BGC)]
###matching feasibility and site series
setkey(feas.list, SS_NoSpace, SppVar)
ss_feas <- merge(ss.list, feas.list, by = "SS_NoSpace", all = T) #%>% dplyr::filter(!Retire == 'x')
ss_NoFeas <- ss_feas[is.na(SppVar),.(SS_NoSpace)]
feas_NoSS <- ss_feas[is.na(BGC),.(SS_NoSpace)]

### matching sibec and site series
# setkey(sibec, SS_NoSpace, Spp)
# ss_feas_sibec <- merge(ss_feas, sibec, by = c("SS_NoSpace","Spp"), all = T)
# 
# sibec_missingSpp <- ss_feas_sibec[,all(is.na(SIPred)), by = Spp][(V1),.(Spp)]
# sibec_missingSS <- ss_feas_sibec[,all(is.na(SIPred)), by = SS_NoSpace][(V1),.(SS_NoSpace)]
# temp <- ss_feas_sibec[(!Spp %in% sibec_missingSpp) & (!SS_NoSpace %in% sibec_missingSS),]
# 
# ##add SIBEC 2013 approximation
# ss_feas_sibec <- merge(ss_feas_sibec, sibec13, by = c("SS_NoSpace","Spp"),all = T)
addSS <- unique(feas_NoSS)
fwrite(addSS, paste0(outFold, "AddSiteSeries.csv"))

outFold <- "./Missing/"
fwrite(bgc_no.model, paste0(outFold, "BGC!modelled.csv"))
fwrite(bgc_no.info, paste0(outFold, "BGC!info.csv"))
fwrite(bgc_NoSS, paste0(outFold, "BGC!SS.csv"))
fwrite(ss_NoBGC, paste0(outFold, "SS!BGC.csv"))
fwrite(ss_NoFeas, paste0(outFold, "SS!Feas.csv"))
fwrite(feas_NoSS, paste0(outFold, "Feas!SS.csv"))

fwrite(asmr_NoBGC, paste0(outFold, "aSMR!BGC.csv"))
fwrite(bgc_NoASMR, paste0(outFold, "BGC!aSMR.csv"))
fwrite(sibec_missingSpp, paste0(outFold, "Feas!SI_Spp.csv"))
fwrite(sibec_missingSS, paste0(outFold, "Feas!SI_SS.csv"))

```

1. There are no BGCs without a matching SS. SS without matching BGCs are `r ss_NoBGC`.
2. There are a lot of SS without matching feasibility entries (`r ss_NoFeas`) and vice versa (`r feas_NoSS`)
3. Understandably, there is a lot of missing SIBEC data. Species which are not included in the dataset are `r sibec_missingSpp`, and site series with no SIBEC data are `r sibec_missingSS`.
4. The edatopic grid matches perfectly with the site series
5. BGCs with no aSMR data: `r bgc_NoASMR`, aSMR without matching BGCs: `r asmr_NoBGC`.
